Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-12-12 Manuscript/manuscript.tex
Added references for our simulations -- only placeholders!! Real links TBA.

MD simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4). The simulation parameters used
in this work are summarized in Table~S1. 
Compatibility with the openMM simulation package \cite{openmm7} was also
tested in SI. 
The simulated trajectories and parameters files are available at \cite{??} \todo{To be uploaded to Zenodo}.

@@

The cationic surfactants were randomly mixed among the phospholipids to form bilayer structures with mole fractions of 10\%, 20\%, 30\%, 42\%, or 50\% of surfactant in the POPC bilayer. All these systems contained 50 POPC molecules per leaflet, 6340 water molecules, and 6, 14, 21, 35, or 50 surfactants per leaflet.  Chloride counter ions were used in simulations, while bromide was the counter ion in the experiment~\cite{scherer89}. For POPC either the Lipid14 with TIP3P~\cite{jorgensen83} or ECC-POPC with SPC/E~\cite{Berendsen1987}  were used. The first 20~ns of the total simulation time of 200~ns was considered as an equilibration time and was omitted from the analysis. Sufficient lipid neighbor exchange occurred during the simulations.
The trajectories and simulation files for unscaled systems are available from
Refs.~\citenum{POPClipid14T313K,POPClipid1410perCATsurfT313K,POPClipid1420perCATsurfT313K,POPClipid1430perCATsurfT313K,POPClipid1442perCATsurfT313K,POPClipid1450perCATsurfT313K}.

\todo{Provide the parameteres for ECC-surfactant somewere.
      Joe: They will appear along with the Zenodo upload of the trajectories.}

>>>>

MD simulations were performed using the GROMACS \cite{Abraham15} simulation package (version 5.1.4). The simulation parameters used
in this work are summarized in Table~S1. 
Compatibility with the openMM simulation package \cite{openmm7} was also
tested in SI. 
The simulated trajectories and parameters files are available at 
Refs.~\citenum{lipid14_POPC_Dang_and_ECC-ions_files, ECC-POPC_nacl_cacl2_files, ECC-POPC_nacl_cacl2_wat-models_files} 
\todo{To be uploaded to Zenodo, references are only placeholders. }.

@@

The cationic surfactants were randomly mixed among the phospholipids to form bilayer structures with mole fractions of 10\%, 20\%, 30\%, 42\%, or 50\% of surfactant in the POPC bilayer. All these systems contained 50 POPC molecules per leaflet, 6340 water molecules, and 6, 14, 21, 35, or 50 surfactants per leaflet.  Chloride counter ions were used in simulations, while bromide was the counter ion in the experiment~\cite{scherer89}. For POPC either the Lipid14 with TIP3P~\cite{jorgensen83} or ECC-POPC with SPC/E~\cite{Berendsen1987}  were used. The first 20~ns of the total simulation time of 200~ns was considered as an equilibration time and was omitted from the analysis. Sufficient lipid neighbor exchange occurred during the simulations.
The simulated trajectories and parameters files are available at Ref.~\citenum{ECC-POPC_cationic-surf_files} 
\todo{To be uploaded to Zenodo, references are only placeholders. }.
The trajectories and simulation files for the unscaled systems are available from
Refs.~\citenum{POPClipid14T313K,POPClipid1410perCATsurfT313K,POPClipid1420perCATsurfT313K,POPClipid1430perCATsurfT313K,POPClipid1442perCATsurfT313K,POPClipid1450perCATsurfT313K}.
